TacticToe: Learning the Game of Tactics

### 2018-02-08 tactictoe_jv.tex
minor

%\title{TacticToe: A theorem prover trained from formal proofs}
%\title{TacticToe: Smart guidance in tactical proof search}
%\title{TacticToe: Proof  by Tactic Selection}
\title{TacticToe: Learning the Game of Tactics}
%\title{TacticToe: Learning the Tactic Game}
%\title{TacticToe: Automatic tactic-level proof generation}

@@

\authorrunning{Gauthier et al.}
%\titlerunning{TacticToe: Learning to Reason with HOL4 Tactics}

@@

\subsection{Initialization}
The input of the algorithm is a goal $g$ that we want to prove.
Therefore the search tree starts with only one node containing the singleton
$g$ and an ordered list of predicted tactics for the goal $g$.
Then, the MCTS algorithm alternates node selection steps and node extension
steps which grow the search tree.

@@

Running the globalized version of a proof script will have the exact same
effect as the original. But since we want to extract information from this
script in the form tactics and their input goals, we modify it further.
In particular, we need to define at which level we should record the tactics of
the proof scripts. The simplest idea would be to record all \sml subexpressions
of type tactics. However, it will damage the quality of our data by
dramatically increasing the number of tactic associated with a single goal.
Imagine a proof script of the form \texttt{A THEN B THEN C} then the tactics
\texttt{A}, \texttt{A THEN B} and \texttt{A THEN B THEN C} would be valid
advice for something close to their common input goal. The tactic
\texttt{A THEN B THEN C} is likely to be specific. In contrast, we can consider
the tactic \texttt{REPEAT A} that is repetitively calling the tactic \texttt{A}
until
\texttt{A} has no effect. In this situation, it is often preferable to record
only \texttt{REPEAT A} and any call to \texttt{A}. Otherwise during the
proof search, we would have to make a branches created after each call of
\texttt{A}.
To sum up, we would like to record only the most general tactics which
make the most progress on a goal. As a trade-off between these two objectives,
we split the proofs into tactic units.

>>>>

%\title{TacticToe: A theorem prover trained from formal proofs}
%\title{TacticToe: Smart guidance in tactical proof search}
%\title{TacticToe: Proof  by Tactic Selection}
\title{TacticToe: Learning the Game of Tactics}
%\title{TacticToe: Automatic tactic-level proof generation}

@@

\authorrunning{Gauthier et al.}
%\titlerunning{TacticToe: Learning the Game of Tactics}

@@

\subsection{Initialization}
The input of the algorithm is a goal $g$ that we want to prove.
Therefore the search tree starts with only one node the list of goals
$[g]$ and an ordered list of predicted tactics for the goal $g$.
Then, the MCTS algorithm alternates node selection steps and node extension
steps which grow the search tree.

@@

Running the globalized version of a proof script will have the exact same
effect as the original. But since we want to extract information from this
script in the form tactics and their input goals, we modify it further.
In particular, we need to define at which level we should record the tactics of
the proof scripts. The simplest idea would be to record all \sml subexpressions
of type tactics. However, it will damage the quality of our data by
dramatically increasing the number of tactic associated with a single goal.
Imagine a proof script of the form \texttt{A THEN B THEN C} then the tactics
\texttt{A}, \texttt{A THEN B} and \texttt{A THEN B THEN C} would be valid
advice for something close to their common input goal. The tactic
\texttt{A THEN B THEN C} is likely to be specific. In contrast, we can consider
the tactic \texttt{REPEAT A} that is repetitively calling the tactic \texttt{A}
until
\texttt{A} has no effect. In this situation, it is often preferable to record
only \texttt{REPEAT A} than calls to \texttt{A}. Otherwise during the
proof search, we would have to make a branches created after each call of
\texttt{A}.
To sum up, we would like to record only the most general tactics which
make the most progress on a goal. As a trade-off between these two objectives,
we split the proofs into tactic units.
